### 2020-02-06 paper/revisions/review-responses.tex

        %--------------------------------------------------------------------
        \question In page 19, why the Pa extraction time was selected to be 30s since Pa is neither the gaseous FPs nor the non-dissolved metals?
        \begin{solution}

        \end{solution}

        %--------------------------------------------------------------------
        \question For Figure 9, it is inaccurate to state that the mass of U-233 reaches equilibrium after ~30 years, apparently from the figure, we can observe that the mass of U-233 for three of the cases still increase/decrease after 30 years.

        \begin{solution}
                Thank you for the excellent point. The statement has been removed from the text.
                Moreover, we rewrite the paragraph to address this thought:\\
                Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ $1.7$ $t$ at the EOL. For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ $35$ and $45$ years for Pu and TRU cases, respectively, decreases. The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt. Hard neutron spectrum converts more $^{233}$U from $^{232}$Th. For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th). However, for $^{233}$U case, the neutron spectrum is hardened at EOL due to the accumulation of Pu isotopes.

@@

        \end{solution}

        %--------------------------------------------------------------------
        \question Regarding to Figure 10, reasons should be provided to explain why the time achieving Pu solubility limit for the case of TRU is shorter than that of the case of reactor-grade Pu.
        \begin{solution}
                 This has now been clarified in the text.
                 We rewrite the paragraph to address this thought:\\
                 Notably, for TRU case, the time achieving Pu solubility limit is shorter than that for reactor-grade Pu case. The reason for this is the relatively high concentration of Pu in the initial heavy metal for the TRU-started SD-TMSR ($\approx$ $29.26$ \% compared with $14.31$ \% for Pu-started SD-TMSR, see Table 5).

@@

        \end{solution}

        %--------------------------------------------------------------------
        \question It is hard to understand that the neutron spectrum of TRU case at BOL is softer than U-233 case since TRU has a greater amount of thermal neutron absorbers and the fissile material is dominated by Pu which would generate hard neutron spectrum.

        \begin{solution}
                 We appreciate your detailed review. 
                 The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U. $^{232}$Th has a very high absorption cross section in the thermal region ($\approx10^2 $b). Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).

                 The following paragraph has been added to the manuscript.\\
                 The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U. $^{232}$Th has a very high absorption cross section in the thermal region ($\approx10^2 $b). Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).

### 2020-02-06 paper/results.tex

In the non-thorium feed mechanism, the SD-TMSR is continuously refueled by heavy metals (Pu and TRU) for 
criticality, which increases the Pu mole concentration (\%) in the molten salt. 
The Pu solubility in FLiBe is 
$\approx$ $4.0$ \% \cite{ignatiev2012progress,sood1975plutonium}. 
Figure~\ref{fig:PusolubilityCC} represents the Pu mole concentration variation in the fuel salt 
for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. In the $^{233}$U and reactor-grade Pu cases, the Pu mole concentration increases 
slightly but still below its solubility limit. On the other hand, the Pu 
mole concentration in the molten salt loaded by TRU increases during operation and 
reaches the Pu solubility limit after $\approx$ $40$ years. This issue may 
be solved by increasing the reactor operation temperature or reducing the 
HM initial inventory \cite{zou2018transition}.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{PusolubilityCC.png}
	\caption{The Pu mole concentration in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:PusolubilityCC}
\end{figure}
\FloatBarrier

@@

\subsection{Neutron spectrum}
Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
lethargy for a full-core SD-TMSR model in the energy range from 10$^{-8}$ to 
10 MeV for the $^{233}$U, reactor-grade Pu, and TRU cases at BOL and EOL. In 
the $^{233}$U case, at the EOL, the neutron spectrum is harder than at BOL due 
to the accumulation of Pu and other strong thermal neutron absorbers in the 
fuel salt. For the reactor-grade Pu and TRU cases, during reactor operation, 
the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
(see Figure~\ref{fig:U233CC}); the neutron spectrum softens and becomes 
similar to the initial thermal spectrum of a $^{233}$U fueled SD-TMSR.
 \begin{figure}
 	\centering
 	\includegraphics[width=1.01\textwidth]{spectrumFLUX110vC.png}
 			\vspace{-0.4in}
 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for 3 different initial 
 		fuel salt compositions (for all cases, the neutron flux
 		confidence intervals $\pm\sigma$ at BOL and EOL are $<1.0139$\% and $<0.6274$\%, respectively).}
 	\label{fig:spectrumFLUX110vC}
\end{figure}

>>>>

In the non-thorium feed mechanism, the SD-TMSR is continuously refueled by heavy metals (Pu and TRU) for 
criticality, which increases the Pu mole concentration (\%) in the molten salt. 
The Pu solubility in FLiBe is 
$\approx$ $4.0$ \% \cite{ignatiev2012progress,sood1975plutonium}. 
Figure~\ref{fig:PusolubilityCC} represents the Pu mole concentration variation in the fuel salt 
for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. In the $^{233}$U and reactor-grade Pu cases, the Pu mole concentration increases 
slightly but still below its solubility limit. On the other hand, the Pu 
mole concentration in the molten salt loaded by TRU increases during operation and 
reaches the Pu solubility limit after $\approx$ $40$ years. This issue may 
be solved by increasing the reactor operation temperature or reducing the 
HM initial inventory \cite{zou2018transition}. Notably, for TRU case, the time achieving Pu solubility limit is shorter than that for reactor-grade Pu case. The reason for this is the relatively high concentration of Pu in the initial heavy metal for the TRU-started SD-TMSR ($\approx$ $29.26$ \% compared with $14.31$ \% for Pu-started SD-TMSR, see Table~\ref{tab:table5}).

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{PusolubilityCC.png}
	\caption{The Pu mole concentration in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:PusolubilityCC}
\end{figure}
\FloatBarrier

@@

\subsection{Neutron spectrum}
Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
lethargy for a full-core SD-TMSR model in the energy range from 10$^{-8}$ to 
10 MeV for the $^{233}$U, reactor-grade Pu, and TRU cases at BOL and EOL. In 
the $^{233}$U case, at the EOL, the neutron spectrum is harder than at BOL due 
to the accumulation of Pu and other strong thermal neutron absorbers in the 
fuel salt. For the reactor-grade Pu and TRU cases, during reactor operation, 
the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
(see Figure~\ref{fig:U233CC}); the neutron spectrum softens and becomes 
similar to the initial thermal spectrum of a $^{233}$U fueled SD-TMSR.
The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U. $^{232}$Th has a very high absorption cross section in the thermal region ($\approx10^2 $b). Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).
 \begin{figure}
 	\centering
 	\includegraphics[width=1.01\textwidth]{spectrumFLUX110vC.png}
 			\vspace{-0.4in}
 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for 3 different initial 
 		fuel salt compositions (for all cases, the neutron flux
 		confidence intervals $\pm\sigma$ at BOL and EOL are $<1.0139$\% and $<0.6274$\%, respectively).}
 	\label{fig:spectrumFLUX110vC}
\end{figure}
